---
title: "Credit card case study"
author: "Jashwanth Neeli"
date: "19/07/2021"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```



```{r}
require(dplyr)
require(lubridate)
require(ggplot2)
```

####  BUSINESS PROBLEM: 
#### In order to effectively produce quality decisions in the modern credit card 
#### industry, knowledge must be gained through effective data analysis and 
#### modeling. Through the use of dynamic data-driven decision-making tools and 
#### procedures, information can be gathered to successfully evaluate all aspects of 
#### credit card operations. 
#### PSPD Bank has banking operations in more than 50 countries across the globe. 
#### Mr. Jim Watson, CEO, wants to evaluate areas of bankruptcy, fraud, and 
#### collections, respond to customer requests for help with proactive offers and 
#### service.


#### DATA AVAILABLE - 

#### This book has the following sheets: 
#### Customer Acquisition: At the time of card issuing, company maintains 
#### the details of customers. 
#### Spend (Transaction data): Credit card spend for each customer 
#### Repayment: Credit card Payment done by customer 
#### Following are some of Watson's questions to a Consultant (like you) to 
#### understand the customers spend & repayment behavior. 


```{r}

setwd("C:/R_Aug/case_study2_CreditCard")

file1 = read.csv("CustomerAcqusition.csv")
file2 = read.csv("spend.csv")
file3 = read.csv("Repayment.csv")

```


###THERE IS AN EMPTY COLUMN IN REPAYMENT DATA
###REMOVE EMPTY DATA FROM THE COLUMN 

```{r}

file3$X <- NULL

```



##Check for NA VALUE

```{r}

sum(is.na(file1))
sum(is.na(file2))
sum(is.na(file3))

```

### 1. In the above dataset, 
##a. Incase age is less than 18, replace it with mean of age values. 

```{r}

mean_Age <-mean(file1$Age)

file1$Age[file1$Age<18]<- mean_Age
file1$Age

```


##b. Incase spend amount is more than the limit, replace it with 50% of that 
##customer's limit. (customer's limit provided in acquisition table is the per 
##                   transaction limit on his card) 

```{r}

Customer_Spent <- dplyr::left_join(file1, file2, by = "Customer")  
Amount <- ifelse(Customer_Spent$Amount>Customer_Spent$Limit, Customer_Spent$Limit/2, Customer_Spent$Amount)
Customer_Spent$Amount <- Amount
```



##c. Incase the repayment amount is more than the limit, replace the 
## repayment with the limit

```{r}

Customer_Repayment <- dplyr::left_join(file1, file3, by = "Customer") 
Amount <- ifelse(Customer_Repayment$Amount>Customer_Repayment$Limit, Customer_Repayment$Limit, Customer_Repayment$Amount)
Customer_Repayment$Amount <- Amount

```



###2. From the above dataset create the following summaries: 


##  a. How many distinct customers exist? 

```{r}

#using dplyr method :

distinct_cust <- dplyr::distinct(file1, Customer)
count(distinct_cust)

```



###b. How many distinct categories exist? 

```{r}

distinct_cat <- file1%>% dplyr::group_by(Segment)%>% summarise(cnt=n())
distinct_cat

```



### c. What is the average monthly spend by customers? 

```{r}

Customer_Spent$Month <-  lubridate::dmy(Customer_Spent$Month)

Customer_Spent$YEAR <- lubridate::year(Customer_Spent$Month)

Customer_Spent$MON_TH <- lubridate::month(Customer_Spent$Month, label = TRUE)

Average_monthly_Spent <- Customer_Spent %>% dplyr::group_by(YEAR,MON_TH) %>% dplyr::summarise(Average_Monthly_Spent = mean(Amount))
Average_monthly_Spent

```



####  d. What is the average monthly repayment by customers?

```{r}

Customer_Repayment$Month <-  lubridate::dmy(Customer_Repayment$Month)
Customer_Repayment$YEAR <- lubridate::year(Customer_Repayment$Month)
Customer_Repayment$MON_TH <- lubridate::month(Customer_Repayment$Month, label = TRUE)
Average_monthly_Repayment <- Customer_Repayment %>% dplyr::group_by(YEAR,MON_TH) %>% dplyr::summarise(Average_Monthly_Repayment =mean(Amount))
Average_monthly_Repayment

```



####  e. If the monthly rate of interest is 2.9%, what is the profit for the bank for 
#### each month? (Profit is defined as interest earned on Monthly Profit. 

```{r}

monthly_Spent <- Customer_Spent %>% dplyr::group_by(YEAR,MON_TH) %>% dplyr::summarise(Average_Monthly = sum(Amount))
monthly_Repayment <- Customer_Repayment %>% dplyr::group_by(YEAR,MON_TH) %>% dplyr::summarise(Average_Monthly = sum(Amount))
For_Profit <- cbind(monthly_Spent, monthly_Repayment)
For_Profit <- dplyr::rename(For_Profit, "SPENT" = "Average_Monthly...3", "REPAY" = "Average_Monthly...6")
For_Profit <- dplyr::rename(For_Profit, "YEAR" = "YEAR...1", "MONTH" = "MON_TH...2")

##DROP USELESS COLUMN

For_Profit$YEAR...4 <- NULL
For_Profit$MON_TH...5 <- NULL

For_Profit$PROFIT <- For_Profit$REPAY- For_Profit$SPENT

PROFIT_PLUS <- For_Profit[For_Profit$PROFIT > 0, ]



PROFIT_PLUS$Profit_AMOUNT <- (PROFIT_PLUS$PROFIT*2.9)/100
PROFIT_PLUS
```




####  f. What are the top 5 product types? 

```{r}

sum_prod_types <- file2 %>% dplyr::group_by(Type) %>% summarise(total = n()) %>% arrange(desc(total))
top5_prod_types <- head(sum_prod_types,5)
top5_prod_types

```



####  g. Which city is having maximum spend? 
    
###### Customer Spent Data is Used For Solution 

```{r}

max_city_spend <- Customer_Spent %>% dplyr::group_by(City) %>% dplyr::summarise(Total_Spend = 
                                                sum(Amount), Percentage = 
           round(sum(Amount)*100/sum(Customer_Spent$Amount),2) ) %>% dplyr::arrange(desc(Total_Spend))
max_city_spend

```



#### h. Which age group is spending more money?  (Age Group 18-36,36-54,54-72,72+)

```{r}

Customer_Spent$Age_group <- ifelse(Customer_Spent$Age<36, "YOUNG", ifelse(Customer_Spent$Age <54, "MID_AGE", ifelse(Customer_Spent$Age <72, "MATURE", "OLD")))
Age_group_spend <- Customer_Spent %>% group_by(Age_group)%>%summarise(ttl_spend = sum(Amount), percentage= round(sum(Amount)*100/sum(Customer_Spent$Amount),2))%>%arrange(desc(ttl_spend))

Age_group_spend

```



####  i. Who are the top 10 customers in terms of repayment?

```{r}


  Top_Customers <- Customer_Repayment %>% dplyr::group_by(Customer) %>% dplyr::summarise(Total_Repayment = 
                                                         sum(Amount)) %>% dplyr::arrange(desc(Total_Repayment))
  Top_10_Customers <- head(Top_Customers,10)
  Top_10_Customers


```



#### 3. Calculate the city wise spend on each product on yearly basis. Also include a 
####  graphical representation for the same. 

```{r}

citywise_spend <- Customer_Spent %>%dplyr::group_by(YEAR,City,Product)%>% summarise(spend = sum(Amount))

require(ggplot2)

ggplot2::ggplot(data = citywise_spend) + aes(x= City, y = spend, fill = Product) + geom_bar(stat = "identity", position = "dodge") + facet_grid(.~YEAR)



```



#### 4. Create graphs for 

####  a. Monthly comparison of total spends, city wise 

```{r}

monthly_citySpend <- Customer_Spent %>% group_by(City, MON_TH) %>% summarise(monthly_spend = sum(Amount))

#using Bar Chart
ggplot2::ggplot(data = monthly_citySpend) + aes(x= MON_TH, y= monthly_spend, fill = City) + geom_bar(stat = "identity", position = "dodge")  

#using line chart
monthly_citySpend %>% ggplot(aes(x= MON_TH, y = monthly_spend, group = City, color = City)) + geom_line() 


```



####  b. Comparison of yearly spend on air tickets 

```{r}

airtickets <- Customer_Spent[Customer_Spent$Type == "AIR TICKET",]
yearly_spend <- airtickets %>% group_by(YEAR, Type) %>% summarise(ttl_spend = sum(Amount))

#using Bar Chart
ggplot2::ggplot(data = yearly_spend) + aes(x= YEAR, y= ttl_spend) + geom_bar(stat = "identity", fill= "red", color = "black", position = "dodge")

#using line chart
yearly_spend %>% ggplot(aes(x= YEAR, y = ttl_spend, color = Type)) + geom_line() + theme_dark()


```



####  c. Comparison of monthly spend for each product (look for any seasonality that exists in terms of spend) 

```{r}

monthly_ProductSpend <- Customer_Spent %>% group_by(Product, MON_TH) %>% summarise(monthly_spend = sum(Amount))

ggplot2::ggplot(data = monthly_ProductSpend) + aes(x= MON_TH, y = monthly_spend, fill = Product) + geom_bar(stat = "identity", position = "dodge") 


```



#### 5. Write user defined R function to perform the following analysis: 
#### You need to find top 10 customers for each city in terms of their repayment 
#### amount by different products and by different time periods i.e. year or 
#### month. The user should be able to specify the product 
#### (Gold/Silver/Platinum) and time period (yearly or monthly) and the function 
#### should automatically take these inputs while identifying the top 10 
#### customers.

```{r}


UDF_TOP10 <- function(Time,Prod) { 
  P_DATA =   Customer_Repayment[(Customer_Repayment$Product == Prod) & ((Customer_Repayment$YEAR = Time) & (Customer_Repayment$MON_TH == Time)),]
  require(dplyr)
  Pre_Result = P_DATA %>% dplyr::group_by(Customer, City, Product, Time) %>% dplyr::summarise(TOTALS_PEND = sum(Amount)) %>% dplyr::arrange(desc(TOTALS_PEND))
  Result = head(Pre_Result,10)
  print(Result) 
  
}

```


```{r}

Product_category = readline(prompt = "Product category should be in Gold/Silver/Platinum: ");
Prod = as.character(Prod);
Time = readline(prompt = "Time Period and time period should be in Year/month: ");
Time = as.integer(Time)

```


```{r}
UDF_TOP10(Time, Prod)
UDF_TOP10

```

